Self Regulation Ontology Retest Data Report

### 2018-03-03 code/SRO_Report.Rmd
adding new plots

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=key, color=task))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.title = element_blank())+
  scale_fill_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    values=c("grey65", "grey45", "grey25"))+
  scale_color_discrete(guide = FALSE)+
  xlab("")+
  ylab("Percent")

@@

@@

The type of ICC we have chosen does not take ... in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.

Had we chosen another kind of ICC taking ... into account could have suggested that tasks have ...(higher/lower) reliability.

@@

To check whether a

first check if the effect of time is significant
compute confidence intervals and check what percent of participants have scores that fall out of this range

```{r}
boot_df
```

>>>>

p5_t <- tmp %>%
  filter(task == 'survey') %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
  geom_violin(fill='#F8766D', position = 'identity')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=43))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

@@

Example of the overlaying procedure.

```{r}
p1<- tmp %>%
  filter(grepl('selection_optimization', dv)) %>%
ggplot(aes(x = var, y = icc)) + 
  geom_violin(fill='#F8766D')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p2<- tmp %>%
  filter(grepl('selection_optimization', dv)) %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc, group=dv)) + 
  geom_violin(fill='#F8766D', position = 'identity')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p3<- tmp %>%
  filter(grepl('selection_optimization', dv)) %>%
ggplot(aes(x = factor(task_group, levels=rev(unique(task_group))), y = icc)) + 
  geom_violin(fill='#F8766D', position = 'identity')+
  theme_bw() + 
  theme(axis.text.y = element_text(size=30))+
  xlab("")+
  ylab("")+
  scale_y_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 15))+
  geom_hline(yintercept = 0, color = "red", size = 1)+
  coord_flip()

p4 <- arrangeGrob(p1,p2, p3,nrow=1)

ggsave('Bootstrap_Example_Plot_t.jpg', plot = p4, device = "jpeg", path = "../output/figures/", width = 41, height = 5, units = "in", limitsize = FALSE, dpi = 100)
```

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Example_Plot_t.jpg')
```

```{r}
rm(p1, p2, p3, p4)
```

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  ggplot(aes(factor(task, levels=c("task","survey"), labels=c("Task", "Survey")), value, fill=task, alpha=key))+
  geom_boxplot()+
  theme_bw()+
  theme(legend.title = element_blank())+
  scale_alpha_manual(breaks = c("var_subs_pct", "var_ind_pct", "var_resid_pct"),
                    labels = c("Variance between individuals",
                               "Variance between sessions",
                               "Error variance"),
                    values=c(0.1, 0.5, 1))+
  scale_fill_discrete(guide = FALSE)+
  guides(alpha=guide_legend(override.aes=list(fill=hcl(c(15,195),100,0,alpha=c(0.1,0.5, 1)),
                                              colour=NA)))+
  xlab("")+
  ylab("Percent")

@@

```{r}
tmp %>%
  gather(key, value, -dv, -task) %>%
  group_by(task, key) %>%
  summarise(mean_pct = mean(value),
            sd_pct = sd(value))
```

@@

The type of ICC we have chosen does not take within subject (between session/systematic) variance in to account. This is why Weir recommends checking whether there is a significant change based on time and examining the SEMs.

Had we chosen another kind of ICC taking this source of variance into account (e.g. 2,1 or 2,k) they could have suggested that tasks have lower reliability.

@@

To check whether a measure shows learning effects in a meaningful number of bootstrapped samples we can: check if the effect of time is significant in each bootstrapped sample and filter variables that have more than 5% of the boostrapped samples showing significant time effects.

Another way might be to compute confidence intervals using SEMs as described in the second half of Weir (2005) and check what percent of participants have scores that fall out of this range. I haven't pursued this at least for now.

Here we ask: Which variables have significant time effects in more than 5% of the bootstrapped samples?

22/74 survey measures
135/335 task measures

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n())
```
